---
title: "Comparing Renewable Energy Development on BLM and Private Land"
author: "Arian Dehnow"
date: "2023-11-27"
output:
  html_document:
    df_print: paged
  pdf_document:
    template: "my-template.tex"
    extra_dependencies:
    - booktabs
    - adjustbox
    keep_tex: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Clear workspace.
rm(list=ls())
gc()
```

```{r packages, include = FALSE}
# Download required packages.
update.packages(repos = "http://cran.us.r-project.org")
if(!require("R.utils")) install.packages("R.utils", repos = "http://cran.us.r-project.org")
if(!require("plyr")) install.packages("plyr", repos = "http://cran.us.r-project.org")
if(!require("dplyr")) install.packages("dplyr", repos = "http://cran.us.r-project.org")
if(!require("sf")) install.packages("sf", repos = "http://cran.us.r-project.org")
if(!require("raster")) install.packages("raster", repos = "http://cran.us.r-project.org")
if(!require("exactextractr")) install.packages("exactextractr", repos = "http://cran.us.r-project.org")
if(!require("ggplot2")) install.packages("ggplot2", repos = "http://cran.us.r-project.org")
if(!require("viridis")) install.packages("viridis", repos = "http://cran.us.r-project.org")
if(!require("tmap")) install.packages("tmap", repos = "http://cran.us.r-project.org")
if(!require("RColorBrewer")) install.packages("RColorBrewer", repos = "http://cran.us.r-project.org")
if(!require("shinyjs")) install.packages("shinyjs", repos = "http://cran.us.r-project.org")
if(!require("leaflet")) install.packages("leaflet", repos = "http://cran.us.r-project.org") 
if(!require("dplyr")) install.packages("dplyr", repos = "http://cran.us.r-project.org") 
if(!require("sf")) install.packages("sf", repos = "http://cran.us.r-project.org") 
if(!require("osmdata")) install.packages("osmdata", repos = "http://cran.us.r-project.org")
if(!require("ggplot2")) install.packages("ggplot2", repos = "http://cran.us.r-project.org") 
if(!require("ggmap")) install.packages("ggmap", repos = "http://cran.us.r-project.org")
if(!require("RColorBrewer")) install.packages("RColorBrewer", repos = "http://cran.us.r-project.org")
if(!require("lintr")) install.packages("lintr", repos = "http://cran.us.r-project.org")
if(!require("cowplot")) install.packages("cowplot", repos = "http://cran.us.r-project.org")
if(!require("tidyr")) install.packages("tidyr", repos = "http://cran.us.r-project.org")
if(!require("tidyverse")) install.packages("tidyverse", repos = "http://cran.us.r-project.org")
if(!require("broom")) install.packages("broom", repos = "http://cran.us.r-project.org")
if(!require("BAMMtools")) install.packages("BAMMtools", repos = "http://cran.us.r-project.org")
if(!require("basemaps")) install.packages("basemaps", repos = "http://cran.us.r-project.org")
if(!require("gstat")) install.packages("gstat", repos = "http://cran.us.r-project.org")
if(!require("fixest")) install.packages("fixest", repos = "http://cran.us.r-project.org")
if(!require("car")) install.packages("car", repos = "http://cran.us.r-project.org")
if(!require("spdep")) install.packages("spdep", repos = "http://cran.us.r-project.org")
if(!require("stars")) install.packages("stars", repos = "http://cran.us.r-project.org")
if(!require("plm")) install.packages("plm", repos = "http://cran.us.r-project.org")
if(!require("modelr")) install.packages("modelr", repos = "http://cran.us.r-project.org")
if(!require("foreign")) install.packages("foreign", repos = "http://cran.us.r-project.org")
if(!require("gplots")) install.packages("gplots", repos = "http://cran.us.r-project.org")
if(!require("stargazer")) install.packages("stargazer", repos = "http://cran.us.r-project.org")
if(!require("tinytex")) install.packages("tinytex", repos = "http://cran.us.r-project.org")
if(!require("pdftools")) install.packages("pdftools", repos = "http://cran.us.r-project.org")
if(!require("formatR")) install.packages("formatR", repos = "http://cran.us.r-project.org")

library(gstat)
library(tidyr)
library(rgdal)
library(rstudioapi)
library(shinyjs)
library(sf)
library(plyr)
library(raster)
library(dplyr)
library(spData)
library(rgdal)
library(raster)
library(rgeos)
library(tmap)
library(ggplot2)
library(ggmap)
library(magrittr)
library(lintr)
library(tidyverse)
library(viridis) # viridis color scale
library(cowplot) # stack ggplots
library(rmarkdown)
library(ggspatial) #use to add arrow and scale bar
library(raster)
library(rgeos)
library(mapview)
library(gstat)
library(fixest)
library(lwgeom)
library(car)
library(spdep)
library(stars)
library(plm)
library(modelr)
library(foreign)
library(gplots)
library(stargazer)
library(tinytex)
library(pdftools)
library(formatR)

setwd("/Users/arian/coding_sample")
df <- file.path("/Users/arian/coding_sample")

```

```{r, include=FALSE}
options(tinytex.verbose = TRUE)

# The style of the table
my_style = style.tex("aer", model.format = "(i)")

# markdown = TRUE is only useful in Rmarkdown documents
setFixest_etable(style.tex = my_style, markdown = TRUE, page.width = "a4")

```

### Import 25-square-kilometer spatial grid that combines spatial data on land ownership and solar and wind energy suitability with a panel data set on solar and wind generators installed across the western states from 1975-2020.

```{r prepare data, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
grid_long <- read_csv(file.path(df, "grid_25km2_long_081622.csv"))

```

### Create factor variables.
```{r, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
grid_long$year=as.factor(grid_long$year)
grid_long$state=as.factor(grid_long$state)
grid_long$county=as.factor(grid_long$county)
grid_long$rent_zone_16_20=as.factor(grid_long$rent_zone_16_20)
```

### Create a dummy variable for Designated Leasing Area (DLA) if a grid cell is classified as DFA, REDA, or SEZ. 

```{r, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
grid_long <- grid_long %>%
  mutate(DLA = ifelse(DFA==1|REDA==1|SEZ==1,1,0))
```

### Filter data set to only cells containing BLM and private land and convert decimal percentages to integers. 

```{r, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
grid_blm <- grid_long %>%
  filter(BLM == 1 | Private==1) %>%
  rename(percent_blm = perc_blm) %>%
  mutate(percent_public = percent_public * 100) %>%
  mutate(percent_blm = percent_blm * 100) %>%
  mutate(percent_dla = percent_dla * 100) %>%
  mutate(percent_solar_exc = percent_solar_exc * 100) %>%
  mutate(percent_wind_exc = percent_wind_exc * 100) %>%
  drop_na(county)
```

### Subset to observations from 2005-2020
```{r 2005, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
grid_2005 <- grid_blm %>%
  filter(as.integer(year) >= 31)
```

### Create solar dataset that excludes grid cells without solar suitability information.
```{r, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
grid_2005_solar <- grid_2005 %>%
  filter(!is.na(solar_GHI.y))
```

### Create wind dataset that excludes grid cells without wind suitability information.
```{r, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
grid_2005_wind <- grid_2005 %>%
  filter(!is.na(wind_windspeed120m))
```

### Create solar data subset containing only grid cells with high solar potential.
```{r, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
grid_2005_high_solar <- grid_2005 %>%
  filter(solar_GHI.y >= 5)
```

### Create wind data subset containing only grid cells with high wind potential.
```{r, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
grid_2005_high_wind <- grid_2005 %>%
  filter(wind_windspeed120m >= 6)
```

### Create solar data subset containing only grid cells within 3km of a border between BLM and private land. 
```{r, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
grid_2005_solar_borders <- grid_2005_solar %>%
  filter(distancetoborder <= 3)
```

### Create wind data subset containing only grid cells within 3km of a border between BLM and private land. 
```{r, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
grid_2005_wind_borders <- grid_2005_wind %>%
  filter(distancetoborder <= 3)
```

### Lighten the load.
```{r, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
rm(grid_blm,grid_long,grid_2005)
gc()
```

### Run solar regressions with different controls and fixed effects.
```{r, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
solar_2005_1 <- feols(MWsolar ~ percent_blm|year, data = grid_2005_solar, se = "hetero")

solar_2005_2 <- feols(MWsolar ~ percent_blm|year + state, data = grid_2005_solar, se = "hetero")

solar_2005_3 <- feols(MWsolar ~ percent_blm + solar_capacity_MW + solar_GHI.y + solar_distance_transmission + distancetoborder|year + state, data = grid_2005_solar, se = "hetero")

solar_2005_4 <- feols(MWsolar ~ percent_blm + solar_capacity_MW + solar_GHI.y + solar_distance_transmission + distancetoborder + percent_solar_exc|year + state, data = grid_2005_solar, se = "hetero")

solar_2005_5 <- feols(MWsolar ~ percent_blm + solar_capacity_MW + solar_GHI.y + solar_distance_transmission + distancetoborder + percent_solar_exc|year + county, data = grid_2005_solar, se = "hetero")

solar_2005_6 <- feols(MWsolar ~ percent_blm + solar_capacity_MW + solar_GHI.y + solar_distance_transmission + distancetoborder + percent_solar_exc|year + state, data = grid_2005_high_solar, se = "hetero")

solar_2005_7 <- feols(MWsolar ~ percent_blm + solar_capacity_MW + solar_GHI.y + solar_distance_transmission + distancetoborder + percent_solar_exc|year + state, data = grid_2005_solar_borders, se = "hetero")
```

### Calculate means.
```{r}
mean(grid_2005_solar$MWsolar)
mean(grid_2005_high_solar$MWsolar)
mean(grid_2005_solar_borders$MWsolar)
```

### Publish a table of results.
```{r results = 'asis', tidy=TRUE, tidy.opts=list(width.cutoff=60)}
etable(solar_2005_1,solar_2005_2,solar_2005_3,solar_2005_4,solar_2005_5,solar_2005_6,solar_2005_7, adjustbox= TRUE)

```

### Lighten the load.
```{r, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
rm(grid_2005_solar,grid_2005_high_solar,grid_2005_solar_borders)
gc()
```

### Run wind regressions with different controls and fixed effects. 
```{r, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
wind_2005_1 <- feols(MWwind ~ percent_blm|year, data = grid_2005_wind, se = "hetero")

wind_2005_2 <- feols(MWwind ~ percent_blm|year + state, data = grid_2005_wind, se = "hetero")

wind_2005_3 <- feols(MWwind ~ percent_blm + wind_capacity_MW + wind_speed_100m + wind_windspeed120m + wind_distance_transmission + distancetoborder|year + state, data = grid_2005_wind, se = "hetero")

wind_2005_4 <- feols(MWwind ~ percent_blm + wind_capacity_MW + wind_speed_100m + wind_windspeed120m + wind_distance_transmission + distancetoborder + percent_wind_exc|year + state, data = grid_2005_wind, se = "hetero")

wind_2005_5 <- feols(MWwind ~ percent_blm + wind_capacity_MW + wind_speed_100m + wind_windspeed120m + wind_distance_transmission + distancetoborder + percent_wind_exc|year + county, data = grid_2005_wind, se = "hetero")

wind_2005_6 <- feols(MWwind ~ percent_blm + wind_capacity_MW + wind_speed_100m + wind_windspeed120m + wind_distance_transmission + distancetoborder + percent_wind_exc|year + state, data = grid_2005_high_wind, se = "hetero")

wind_2005_7 <- feols(MWwind ~ percent_blm + wind_capacity_MW + wind_speed_100m + wind_windspeed120m + wind_distance_transmission + distancetoborder + percent_wind_exc|year + state, data = grid_2005_wind_borders, se = "hetero")
```

### Calculate means.
```{r, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
mean(grid_2005_wind$MWwind)
mean(grid_2005_high_wind$MWwind)
mean(grid_2005_wind_borders$MWwind)
```

### Publish a table of results.
```{r results = 'asis', tidy=TRUE, tidy.opts=list(width.cutoff=60)}
etable(wind_2005_1,wind_2005_2,wind_2005_3,wind_2005_4,wind_2005_5,wind_2005_6,wind_2005_7,adjustbox= TRUE)
```